---
title: "Airbnb"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---
Page 1
=========================================================================


```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(datasets)
library(shiny)
library(dplyr)
library(tidyverse)
library(bindr)
library(ggplot2)
library(viridis)
library(ggmap)
library(rgdal)
library(Hmisc)
library(Metrics)
library(corrr)
library(ade4)
library(data.table)
library(scales)
library(viridis)
library(flexdashboard)
data(iris)
df  <- read.csv("listings.csv")
register_google(key = "AIzaSyD8zedZOWspc5a_a1T4iB1zCudOx8I3V-k")
```


Column {.sidebar}
-----------------------------------------------------------------------

```{r}
radioButtons('x', 'X Variable', c("year","month","day"))

```

Column
-----------------------------------------------------------------------


```{r}
df  <- read.csv("listings.csv")
df <- df %>%
  select(c('host_since','price','room_type','bedrooms','property_type','host_verifications', 'latitude', 'longitude',"beds","accommodates","bathrooms"))
df <- df %>%
  filter(!is.na(host_since) & !is.na(price))%>%
   mutate(bedrooms  = ifelse(is.na(bedrooms), as.integer(mean(df$bedrooms, na.rm = TRUE)), bedrooms))%>%
mutate(price = as.double(gsub("\\$", "",price)))

df$host_since <-as.POSIXct(strptime(df$host_since, "%m/%d/%Y", "GMT"))

df <- df %>%
  mutate(month = format(host_since, "%m"), year = format(host_since, "%Y"), day = format(host_since, "%d"))
df <- df %>%
  filter(!is.na(host_since) & !is.na(price))

montly_count <- df%>%
  group_by(month)%>%
  summarise(Count = n())%>%
  ggplot(aes(x=month,y=Count)) + geom_bar(stat = "identity")

```

### Number of registractions and Mean rent of Properties. 
```{r}

aggregated <- reactive({
  df%>%
  group_by_(input$x)%>%
  summarise(Count = n(), Mean_Price = mean(price)*10)%>%
  melt(c('Count','Mean_Price'),id.vars = 1)%>%
  ggplot(aes_string(x=input$x,y = "value")) + 
    geom_bar(aes(fill = variable),stat = "identity",position = "dodge")+scale_y_continuous(
    "Count", 
    sec.axis = sec_axis(~ . /10, name = "Mean Price")
  )
  
})
renderPlot({
  aggregated()
})
```


Page 2
========================================================

row {.tabset}
-----------------------------------------------------


### Average rent of property by room type.

```{r}

df%>%
  group_by(room_type)%>%
  summarise(mean_of_price = mean(price, na.rm = TRUE))%>%
  ggplot(aes(x= "", fill= room_type, y= mean_of_price)) + geom_bar(stat='identity') + coord_polar("y", start=0)

```

### Number of property by room type.

```{r}

df%>%
  group_by(room_type)%>%
  summarise(count = n())%>%
  ggplot(aes(y = count, x = room_type, fill = room_type)) + geom_bar(stat='identity') + coord_polar("y", start=0)


```

Row
------------------------------------------------------

### Number of bedrooms in the property V/S Mean Price of property and number of properties 

```{r}

df %>%
  group_by(bedrooms)%>%
  summarise(Count = n(), Mean_Price = mean(price)*10)%>%
  melt(c('Count','Mean_Price'),id.vars = 1)%>%
  ggplot(aes(x = bedrooms,y = value)) + geom_bar(aes(fill = variable),stat = "identity",position = "dodge")+scale_y_continuous( "Count",  sec.axis = sec_axis(~ . /10, name = "Mean Price"))


```

### Relation between host verification and the Rent for the property

```{r}
df %>%
  mutate(host_verifications = str_count(host_verifications, "'")/2)%>%
  group_by(host_verifications)%>%
  summarise(mean = mean(price))%>%
  ggplot(aes(host_verifications, mean)) +geom_line(size = 2, color = "#A45D4E") + ylab("mean price $")
```

Row {data-height=30}
-----------------------------------------------------------------------
Rent of 5 most expensive properties.

Row 
-----------------------------------------------------------------------

### Private room in lighthouse

```{r}
lighthouse <- df%>%
  filter(property_type == "Private room in lighthouse")%>%
  summarise(mean(price))
gauge(lighthouse[1,1], min = 0, max = 1000, gaugeSectors(
  success = c(0, 500), warning = c(500, 699), danger = c(700, 1000)
))

```

### Entire resort

```{r}
lighthouse <- df%>%
  filter(property_type == "Entire resort")%>%
  summarise(round(mean(price, na.rm = TRUE),2))

gauge(lighthouse[1,1], min = 0, max = 1000, gaugeSectors(
  success = c(0, 500), warning = c(500, 699), danger = c(700, 1000)
))

```

### Private room in tent

```{r}
lighthouse <- df%>%
  filter(property_type == "Private room in tent")%>%
  summarise(mean(price))
gauge(lighthouse[1,1], min = 0, max = 1000, gaugeSectors(
  success = c(0, 500), warning = c(500, 699), danger = c(700, 1000)
))

```

### Private room in resort

```{r}
lighthouse <- df%>%
  filter(property_type == "Private room in resort")%>%
  summarise(mean(price))
gauge(lighthouse[1,1], min = 0, max = 1000, gaugeSectors(
  success = c(0, 500), warning = c(500, 699), danger = c(700, 1000)
))

```

### Entire bed and breakfast

```{r}
lighthouse <- df%>%
  filter(property_type == "Entire bed and breakfast")%>%
  summarise(mean(price))
gauge(lighthouse[1,1], min = 0, max = 1000, gaugeSectors(
  success = c(0, 500), warning = c(500, 699), danger = c(700, 1000)
))

```

Row {data-height=30}
-----------------------------------------------------------------------
Rent of 5 least expensive properties.

Row 
-----------------------------------------------------------------------

### Private room in in-law

```{r}
lighthouse <- df%>%
  filter(property_type == "Private room in in-law")%>%
  summarise(mean(price))
gauge(lighthouse[1,1], min = 0, max = 1000, gaugeSectors(
  success = c(0, 500), warning = c(500, 699), danger = c(700, 1000)
))

```

### Private room in dome house

```{r}
lighthouse <- df%>%
  filter(property_type == "Private room in dome house")%>%
  summarise(mean(price))
gauge(lighthouse[1,1], min = 0, max = 1000, gaugeSectors(
  success = c(0, 500), warning = c(500, 699), danger = c(700, 1000)
))

```

### Private room in dorm

```{r}
lighthouse <- df%>%
  filter(property_type == "Private room in dorm")%>%
  summarise(mean(price))
gauge(lighthouse[1,1], min = 0, max = 1000, gaugeSectors(
  success = c(0, 500), warning = c(500, 699), danger = c(700, 1000)
))

```

### Private room in train

```{r}
lighthouse <- df%>%
  filter(property_type == "Private room in train")%>%
  summarise(mean(price))
gauge(lighthouse[1,1], min = 0, max = 1000, gaugeSectors(
  success = c(0, 500), warning = c(500, 699), danger = c(700, 1000)
))

```

### Shared room in bungalow

```{r}
lighthouse <- df%>%
  filter(property_type == "Shared room in bungalow")%>%
  summarise(mean(price))
gauge(lighthouse[1,1], min = 0, max = 1000, gaugeSectors(
  success = c(0, 500), warning = c(500, 699), danger = c(700, 1000)
))

```


Page 3
=========================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
selectInput('yea', 'Year',c("2012","2016","2013","2019","2014","2018","2015","2017","2020"))
radioButtons('room', 'Room Type',unique(df$room_type) )
```


Column {data-width=350}
-----------------------------------------------------------------------

```{r}

library(shiny)
LA_map <- get_map(location = c(-73.95131,40.72965),
    color = "color",
    source = "google",
    maptype = "satellite",
    zoom = 11)
theme_set(theme_bw(16))

aggregated_map <-reactive({

df_2008 <- df%>%
  filter(year == input$yea)%>%
  filter(room_type == input$room)

ggmap(LA_map,
    extent = "device",
    xlab = "Longitude",
    ylab = "Latitude") +
    
    # Add core lat/long coordinates as points, colored by fraction organic matter
    geom_point(data = df_2008, aes(x = longitude, y = latitude ,alpha = 0.0001, color = price, size = price)) +scale_color_gradientn(" ",colors = c("#EFEC35", "#E82323")) 
    # Provide ggplot2 with color gradient
})

renderPlot({
  aggregated_map()
})
```

Row {data-height=300}
-----------------------------------------------------------------------

### Number of properties registered in selected year

```{r}
aggregated_count <-reactive({
df%>%
  filter(year == input$yea)%>%
  group_by(room_type)%>%
  summarise(count = n())%>%
  ggplot(aes(count,room_type)) + geom_bar(stat = "identity")

})
renderPlot({
  aggregated_count()
})
```

### Total Number of properties registered in selected year 

```{r}
aggregated_count_all <-reactive({
df_total <- df%>%
  filter(year == input$yea)%>%
  summarise(count = n())
return(df_total[1,1])

})


renderGauge({
  gauge(aggregated_count_all(), min = 0, max = 6000,gaugeSectors(
  success = c(0, 2000), warning = c(2001, 4000), danger = c(4000, 6000)))
})


```


Page 4
=========================================================================

Column {.sidebar}
-----------------------------------------------------------------------

```{r}
checkboxInput('ploty', 'Plot Actual Rent', value = FALSE, width = NULL)
checkboxInput('ploty_', 'Plot Predicted Rent', value = FALSE, width = NULL)

```

Column
-----------------------------------------------------------------------

### Predictions 
```{r}
OHE_cols <- c("property_type", "room_type")
df_1 <- df
for (c in OHE_cols){
  df_all_dummy <- acm.disjonctif(df_1[c])
  df_1 <- cbind(df_1, df_all_dummy)

}

df_1 <- df_1 %>%
  select(-c("property_type", "room_type", "bathrooms", "host_since", "month", "year", "day","host_verifications"))


res.cor <- correlate(df_1)
col_names <- res.cor%>%
  select(c("term","price"))%>%
  mutate(price =abs(price))%>%
  filter(price > 0.1)%>%
  select(term)

df_1 <- df_1%>%
  select(c(col_names$term, price))

colnames(df_1) <- c("bed","longitude","beds","accommodates","property_type_Entire_apartment","property_type_Entire_condominium","property_type_Entire_house","property_type_Entire_loft","property_type_Entire_townhouse",
                  "property_type_Private_room_in_apartment","property_type_Private_room_in_house",
                  "property_type_Private_room_in_townhouse",
                  "room_type_Entire_home_apt","room_type_Private_room","price")

library(randomForest)
df_1 <- na.omit(df_1)
smp_size <- floor(0.75 * nrow(df_1))

set.seed(1243)
train_ind <- sample(seq_len(nrow(df_1)), size = smp_size)
train <- df_1[train_ind,]
test <- df_1[-train_ind, ]
rf<-  randomForest(price~., train, ntrees = 200)
predicted <- predict(rf, test)

clusters <- reactive({
  print("react")
  randomForest(price~., train, ntrees = input$ntrees)
})

random_forest_1001 <-reactive({
  print("pppp")
  #rf <- randomForest(price~., train, ntrees = input$ntrees)
  #predicted <- predict(rf,test)
  #ggplot()+geom_line(aes(c(1:10),head(predicted,10)), colour ="green", size =1) +labs(subtitle = "Green -> Y^ \n Red -> Y") + geom_line(aes(c(1:10), head(test$price, 10)), color = "red", size =1)+  xlab("Property") +ylab("Price")  +labs(color = "Y")
    

})

renderPlot({
graph <- ggplot()+labs(subtitle = "Green -> Y^ \n Red -> Y")+  xlab("Property") +ylab("Price")

if (input$ploty == 1)({print("l2")
graph <- graph+geom_line(aes(c(1:100),head(predicted,100)), colour ="green", size =1)
})


if (input$ploty_ == 1)({print("l2")
graph <- graph+geom_line(aes(c(1:100), head(test$price, 100)), color = "red", size =1)
})
print('end')
graph
  })




```

